### 2017-07-12 README.Rmd
Add tweaks

One categorical (>2 level) - GoF  (not yet implemented)
```
mtcars %>%
  specify(response = cyl) %>% # alt: cyl ~ 1
  hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>%
  generate(reps = 100, type = "simulate") %>%
  calculate(stat = "chisq")
```

Two categorical (>2 level) variables  (not yet implemented)
```
mtcars %>%
  specify(cyl ~ am) %>% # alt: response = cyl, explanatory = am
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "chisq")
```

@@

```
mtcars %>%
  specify(mpg ~ am) %>% alt: response = mpg, explanatory = am
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in means")
```

@@

Two numerical vars - SLR  (not yet implemented)
```
mtcars %>%
  specify(mpg ~ hp) %>% alt: response = mpg, explanatory = cyl
  hypothesize(null = "independence") %>% # or "slope = 0"
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "lm(mpg ~ hp)")
```

@@

```
mtcars %>%
  specify(response = mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "mean")
```

One numerical (one proportion)

```
mtcars %>%
  specify(response = mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "mean")
```

>>>>

One categorical (>2 level) - GoF  (not yet implemented)

```
mtcars %>%
  specify(response = cyl) %>% # alt: cyl ~ 1
  hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>%
  generate(reps = 100, type = "simulate") %>%
  calculate(stat = "chisq")
```

Two categorical (>2 level) variables  (not yet implemented)

```
mtcars %>%
  specify(cyl ~ am) %>% # alt: response = cyl, explanatory = am
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "chisq")
```

@@

```
mtcars %>%
  specify(mpg ~ am) %>% # alt: response = mpg, explanatory = am
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in means")
```

@@

Two numerical vars - SLR  (not yet implemented)

```
mtcars %>%
  specify(mpg ~ hp) %>% # alt: response = mpg, explanatory = cyl
  hypothesize(null = "independence") %>% # or "slope = 0"
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "slope")
```

@@

```
mtcars %>%
  specify(response = mpg) %>% # alt: mpg ~ 1
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "mean")
```

One categorical (one proportion) (not yet implemented)

```
mtcars %>%
  specify(response = am) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "prop")
```
